Supplementary Materials

### 2023-07-03 manuscript/supplementary.tex
minor ms changes

  \caption{The distribution of block jackknife samples for the Feature Priority
  model fit on YRI data. The ranges at the top of the figure indicate the
untrimmed and the 2 IQR-trimmed jackknife intervals. for XXX fix fig }

@@

>>>>

  \caption{The distribution of block jackknife samples for the Feature Priority
  model fit on YRI data. The ranges at the top of the figure indicate the
untrimmed and the 2 IQR-trimmed jackknife intervals. Trimming off the numeric
optimization outliers leads to more realistic estimates of uncertainty.}

@@

\subsection{Additional DFE Figures}

\begin{figure}[htbp]
  \label{suppfig:dfe-ceu}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/supplementary/figure_ceu_dfe.pdf}
  \caption{The DFE across models for the CEU reference sample (analogous to the
  DFE for YRI samples in Figure \ref{fig:figure-3}.}
\end{figure}

\begin{figure}[htbp]
    \label{suppfig:dfe-chb}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/supplementary/figure_chb_dfe.pdf}
  \caption{The DFE across models for the CHB reference sample (analogous to the
  DFE for YRI samples in Figure \ref{fig:figure-3}.}
\end{figure}
